### 2022-11-11 files/Chapter5/PlateModel.tex
Checked Chapter 5

\subsubsection{Reference configuration for a rectangular plate}
Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body as $\Omega \in R^2$ with the reference point $(0,0)$. For a rectangular plate, 
\begin{eqnarray*}
	\Omega = \left \{ x \in R_2 \ | \ 0 \leq x_1 \leq 1, \ 0 \leq x_2 \leq b \right \}.
\end{eqnarray*} 
Let $\partial \Omega$ denote the boundary of plate. The boundary $\partial \Omega$ can be divided into four distinct lines.\\

@@

\textcolor{red}{*****************************}\\
Since the plate is a rectangular shape in $R^2$, one would easily try to use the reference configuration as the two-dimensional elastic body in section 5.2. However for the plate model, the space $R^2$ can be considered perpendicular to the space for the two-dimensional elastic body in section 5.2.\\
\textcolor{red}{*****************************}

@@

		\node at (7.2,0.1) {$b$};
		\node at (3.2,-0.27) {$\ell = 1$};

@@

\textcolor{red}{CHECK!!!}
\subsubsection{Bilinear Form}
\begin{eqnarray*}
b(u,\phi) & = & \int_\Omega \boldsymbol{Q} \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,\\
	& + & \frac{1}{\beta(1-\nu^2)}\int_{\Omega} (\partial_1\psi_1 + \nu\partial_2\psi_2)\partial_1\phi_1+ (\partial_2\psi_2 + \nu\partial_1\psi_1)\partial_2\phi_2 \ dA,\\
	& + & \frac{1}{2\beta(1+\nu)}\int_{\Omega} (\partial_1\psi_2+\partial_2\psi_1)(\partial_1\phi_2+\partial_2\psi_1) \ dA.\\
\end{eqnarray*}

@@

\textcolor{red}{INTERPOLATION TERM}

>>>>

\subsubsection{Reference configuration for a rectangular plate}
Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body as $\Omega \in R^2$ with the reference point $(0,0)$. For a rectangular plate,
\begin{eqnarray*}
	\Omega = \left \{ x \in R_2 \ | \ 0 \leq x_1 \leq 1, \ 0 \leq x_2 \leq b \right \}.
\end{eqnarray*}
Let $\partial \Omega$ denote the boundary of plate. The boundary $\partial \Omega$ can be divided into four distinct lines.

@@

\textbf{Remark} The mathematical definition of $R_2$ is the same as the two-dimensional beam. Practically, it is not the same. The plate model is a horisontal two-dimensional plane, and the two-dimensional beam is a vertical two-dimensional plane.

@@

		\node at (7.2,0.1) {$b$};
		\draw[-stealth] (7.25,0.2) -- (8.1,0.7);
		\draw (8,0.7) -- (8.2,0.7);
		\draw[-stealth] (7,0.05) -- (6.7,-0.15);
		\draw (6.6,-0.15) -- (6.8,-0.15);

		\node at (3.2,-0.3) {$1$};
		\draw[stealth-] (-0.8,-0.3) -- (3,-0.3);
		\draw[stealth-] (6.2,-0.3) -- (3.3,-0.3);
		\draw (6.2,-0.2) -- (6.2,-0.4);

@@

\subsubsection{Bilinear Form}
\begin{eqnarray*}
b(u,\phi) & = & \int_\Omega \boldsymbol{Q} \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,\\
	& + & \frac{1}{\beta(1-\nu^2)}\int_{\Omega} (\partial_1\psi_1 + \nu\partial_2\psi_2)\partial_1\phi_1+ (\partial_2\psi_2 + \nu\partial_1\psi_1)\partial_2\phi_2 \ dA,\\
	& + & \frac{1}{2\beta(1+\nu)}\int_{\Omega} (\partial_1\psi_2+\partial_2\psi_1)(\partial_1\phi_2+\partial_2\psi_1) \ dA.\\
\end{eqnarray*}

@@
